Design, Implementation, and Evaluation of Open Power Quality

### 2020-05-28 02-intro.tex
Add opq box section

The remainder of this paper is organized as follows. Sections \ref{sec:system-architecture} and \ref{sec:information-architecture} present an overview of the OPQ system architecture and information architecture. Section \ref{sec:related-work} presents related research and technology.  Section \ref{sec:opq-makai} discusses OPQ Box and its triggering system, and Section \ref{sec:opq-makai} discusses our cloud-based analysis services. Section \ref{sec:pilot} discusses the pilot deployment of a sensor network and its results. Section \ref{sec:conclusions} concludes with some proposals for future research.

>>>>

The remainder of this paper is organized as follows. Sections \ref{sec:system-architecture} and \ref{sec:information-architecture} present an overview of the OPQ system architecture and information architecture. Section \ref{sec:related-work} presents related research and technology.  Section \ref{sec:opq-box} discusses OPQ Box and Section \ref{sec:opq-makai} its triggering system. Section \ref{sec:opq-mauka} describes our analysis services, and Section \ref{sec:opq-view} our user interface.  Section \ref{sec:pilot} discusses the pilot deployment of a sensor network and its results. Section \ref{sec:conclusions} concludes with some proposals for future research.
